Do we need detailed demographic data to forecast plant population responses to climate change?

### 2016-07-11 manuscript/manuscript.Rmd
adds UAES journal paper number
adds data accessibility statement

Acknowledgments
---------------
This work was funded by the National Science Foundation through a Postdoctoral Research Fellowship in Biology to ATT (DBI-1400370), award MSB-1241856 to MBH, and a CAREER award to PBA (DEB-1054040). We thank the original mappers of the permanent quadrats in Montana and the digitizers in the Adler lab, without whom this work would not have been possible. Informal conversations with Stephen Ellner, Giles Hooker, Robin Snyder, and a series of meetings between the Adler and Weecology labs at USU sharpened our thinking. Brittany Teller provided comments that improved our manuscript. Compute, storage and other resources from the Division of Research Computing in the Office of Research and Graduate Studies at Utah State University are gratefully acknowledged. Any use of trade, firm, or product names is for descriptive purposes only and does not imply endorsement by the U.S. government.

>>>>

Acknowledgments
---------------
This work was funded by the National Science Foundation through a Postdoctoral Research Fellowship in Biology to ATT (DBI-1400370), award MSB-1241856 to MBH, and a CAREER award to PBA (DEB-1054040). We thank the original mappers of the permanent quadrats in Montana and the digitizers in the Adler lab, without whom this work would not have been possible. Informal conversations with Stephen Ellner, Giles Hooker, Robin Snyder, and a series of meetings between the Adler and Weecology labs at USU sharpened our thinking. Brittany Teller provided comments that improved our manuscript. Compute, storage and other resources from the Division of Research Computing in the Office of Research and Graduate Studies at Utah State University are gratefully acknowledged. Any use of trade, firm, or product names is for descriptive purposes only and does not imply endorsement by the U.S. government. This research was supported by the Utah Agricultural Experiment Station, Utah State University, and approved as journal paper number 8917.

Data Accessibility
------------------
The data used in this paper have been archived on Ecological Archives: http://esapubs.org/archive/ecol/E092/143/. All data and R code necessary to reproduce our work has been deposited on Dryad (link) and is also available on GitHub (http://github.com/atredennick/MicroMesoForecast).
